Zaca Fire Type Conversion

### 2020-10-07 Model Data Sheets and Code/Manuscript_Code.Rmd
tidy up code

@@

###... Stepwise Variable Selection

@@

```
prediction step, variables selected:all

@@

removed aug_max_vpd2006 and precip_2006 and reran VSURF

interp step: "vpd_aug"      "slope"        "rain"         "tmax"         "tmin_jan"     "tmin_jan2007"

@@

mcf_tc_samplesize <- mcf %>% group_by(tc_mortality) %>%count() #type converted n = 99
mcf_tc_samplesie <- mcf %>% group_by(rdnbr_tc) %>%dplyr::count() # type converted n = 55 (almost too small to use)
mcf_tc_samplesie <- mcf %>% group_by(rdnbr_qualitative) %>%dplyr::count() # high=66, low= 585, moderate=272, type converted n = 84 
mcf_tc_samplesie <- mcf %>% group_by(rdnbr_qualitative) %>%dplyr::summarise(acres = sum(Shape_Area/4047)) %>%dplyr::summarise(tot_acres = sum(acres))

ggplot(mcf, aes(x = rdnbr_tc, y = rdnbr_2007)) +geom_jitter(aes(color=tc_mortality))
ggplot(mcf, aes(x=dnbr_2007, y=rdnbr_2007)) +geom_point(aes(color=tc_mortality)) + geom_hline(yintercept=875)
ggplot(mcf, aes(ndmi_2006, y=evi_2006)) +geom_point()
ggplot(mcf, aes(dem_10m_zaca, y=tmin_jan2007)) +geom_point()
mod <- lm(ndmi_2006~evi_2006, data=mcf) # R2=0.18
mod1 <- lm(dem_10m_zaca~tmin_jan2007, data=mcf) # R2=0.04
mod2 <- lm(dem_10m_zaca~cwd, data=mcf) # R2=0.47
mod3 <- lm(dem_10m_zaca~rain, data=mcf) # R2=0.498
mod4 <- lm(dem_10m_zaca~tmax, data=mcf) # R2=0.5
mod5 <- lm(dem_10m_zaca~vpd_aug, data=mcf) # R2=0.56
mod6 <- lm(tmax~vpd_aug, data=mcf) # R2=0.95
mod7 <- lm(cwd~vpd_aug, data=mcf) # R2=0.53
mod8 <- lm(tmax~cwd, data=mcf) # R2=0.49

mcf %>% dplyr::summarise(min = min(tslf),
                         mean = mean(tslf),
                         median = median(tslf),
                         max = max(tslf), 
                         min_elev = min(dem_10m_zaca),
                         mean_elev = mean(dem_10m_zaca),
                         max_elev = max(dem_10m_zaca))

@@

# select variables to be used in the model
mcf_model <- mcf %>% 
  dplyr::select(rdnbr_tc, tmin_jan2007, tmax, vpd_aug, cwd, rain, sr, slope, aspect_transformed, TWI, ndmi_2006, evi_2006, tslf) # not sure if fri and years so fire, whic sounds like Time Since Last Fire, are the same thing

# run tuneRanger
mcf_task <- makeClassifTask(data = mcf_model, target = "rdnbr_tc")
tune_output <- tuneRanger(mcf_task, 
                          measure = list(mmce), 
                          num.trees = 1500, 
                          tune.parameters = c("mtry", "min.node.size"))

# 4 rdnbr classes
mcf_model3 <- mcf %>% 
  dplyr::select(rdnbr_qualitative, tmin_jan2007, tmax, vpd_aug, cwd, rain, sr, slope, aspect_transformed, TWI, ndmi_2006, evi_2006, tslf) # not sure if fri and years so fire, whic sounds like Time Since Last Fire, are the same thing

@@

3 classes
mtry=9,min.node.size=3; VI is mostly stable!
###... Random Forest
```{r}
for (i in 1:10) {

@@

```
###... ROC/AUC
```{r}
# code: https://stats.stackexchange.com/questions/188616/how-can-we-calculate-roc-auc-for-classification-algorithm-such-as-random-forest
rfm_roc <-  roc(mcf_model$rdnbr_tc, rfm$votes[,2])
plot(rfm_roc)
auc(rfm_roc)
```
###... ALE
```{r}

@@

# predictors 
nlm_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf_ale$rdnbr_qualitative, type = "prob", class="NLM")
high_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf_ale$rdnbr_qualitative, type = "prob", class="High")
tc_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf_ale$rdnbr_qualitative, type = "prob", class="Type Converted")

d = 7
#ndmi
nlm1 <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high1 <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
tc1 <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm1, high1, tc1, nrow=1)
##ggsave(here::here("Graph Images", "mcf ndmi.jpg"))
#theme (panel.background = element_rect(width = 5))

@@

@@

ggarrange(nlm1, nlm2,nlm3,nlm4,nlm5,nlm6,nlm7,nlm8,nlm9,nlm10,nlm11,nlm12, nrow = 3, ncol=4)
ggsave(here::here("Graph Images", "mcf all ulm.jpg"), width=8, height = 8)

ggarrange(high1,high2,high3,high4,high5,high6,high7,high8,high9,high10,high11,high12, nrow=3, ncol=4)
ggsave(here::here("Graph Images", "mcf all high.jpg"), width=8, height = 8)

ggarrange(tc1,tc2,tc3,tc4,tc5,tc6,tc7,tc8,tc9,tc10,tc11,tc12, nrow=3, ncol=4)
ggsave(here::here("Graph Images", "mcf all tc.jpg"), width=8, height = 8)

@@

```{r}
pico <- read_csv("coulter_env_modified.csv") %>% 
  mutate(rdnbr_qualitative = case_when(
    rdnbr_2007 < 640 ~ "NLM",
    rdnbr_2007 < 850 ~ "High",
    rdnbr_2007 >= 850 ~ "Type Converted")) %>%
  mutate(rdnbr_qualitative = as.factor(rdnbr_qualitative),
         rdnbr_qualitative = fct_relevel(rdnbr_qualitative, levels=c("NLM","High", "Type Converted"))) %>% 
  #filter(Mortality != "bigcone") %>% # 60 stands actually have big cones not pico
  dplyr::select(-Mortality, -type_converted, -ndvi_2006) %>% 
  na.omit(pico) %>%  # 56 stands have NA values (probs all very small stands)
   mutate(rdnbr_qualitative2 = case_when(
    rdnbr_qualitative %in% "High" ~ "High",
    rdnbr_qualitative %in% c("Moderate", "Low", "None") ~ "NLM")) %>% 
  mutate(rdnbr_qualitative2 = as.factor(rdnbr_qualitative2)) %>% 
  mutate(rdnbr_qualitative2= fct_relevel(rdnbr_qualitative2, levels=c("NLM", "High"))) %>% 
  mutate(aspect_transformed = (1-cos((2*pi*aspect_30m)/360))/2) %>% 
  mutate(rdnbr_tc = case_when(
    rdnbr_2007 < 850 ~ "Not_TC",
    rdnbr_2007 >= 850 ~ "TC"
  )) %>% 
  mutate(rdnbr_tc = as.factor(rdnbr_tc)) %>% 
  mutate(rdnbr_tc= fct_relevel(rdnbr_tc, levels=c("Not_TC", "TC"))) %>% 
  rename_all(funs(str_replace(., "_30m", "")))

@@

@@

#ndmi
nlm <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("NLM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("High") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
ggsave(here::here("Graph Images", "pico ndmi.jpg"))
#theme (panel.background = element_rect(width = 5))

#solar radiation
nlm <- plot(FeatureEffect$new(nlm_predictor, feature = "insolation")) + ggtitle("NLM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high <- plot(FeatureEffect$new(high_predictor, feature = "insolation")) + ggtitle("High") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc <- plot(FeatureEffect$new(tc_predictor, feature = "insolation")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
ggsave(here::here("Graph Images", "pico sr.jpg"))

>>>>

### ... summary statistics
```{r}
# sample sizes
mcf_tc_samplesize <- mcf %>% group_by(tc_mortality) %>%count() #type converted manual estimates n = 99
mcf_tc_samplesie <- mcf %>% group_by(rdnbr_tc) %>%dplyr::count() # rdnbr=1000 for type converted  n = 55 (almost too small to use)
mcf_tc_samplesie <- mcf %>% group_by(rdnbr_qualitative) %>%dplyr::count() #rdnbr = 850:  high=66, low= 585, moderate=272, type converted n = 84

# acres by burn severity class an dtotal acres
mcf_tc_samplesie <- mcf %>% group_by(rdnbr_qualitative) %>%dplyr::summarise(acres = sum(Shape_Area/4047)) %>%dplyr::summarise(tot_acres = sum(acres))

# look at correlations/trends in potentially correlated variables
ggplot(mcf, aes(x = rdnbr_tc, y = rdnbr_2007)) +geom_jitter(aes(color=tc_mortality))
ggplot(mcf, aes(x=dnbr_2007, y=rdnbr_2007)) +geom_point(aes(color=tc_mortality)) + geom_hline(yintercept=875)
ggplot(mcf, aes(ndmi_2006, y=evi_2006)) +geom_point()
ggplot(mcf, aes(dem_10m_zaca, y=tmin_jan2007)) +geom_point()
mod <- lm(ndmi_2006~evi_2006, data=mcf) # R2=0.18
mod1 <- lm(dem_10m_zaca~tmin_jan2007, data=mcf) # R2=0.04
mod2 <- lm(dem_10m_zaca~cwd, data=mcf) # R2=0.47
mod3 <- lm(dem_10m_zaca~rain, data=mcf) # R2=0.498
mod4 <- lm(dem_10m_zaca~tmax, data=mcf) # R2=0.5
mod5 <- lm(dem_10m_zaca~vpd_aug, data=mcf) # R2=0.56
mod6 <- lm(tmax~vpd_aug, data=mcf) # R2=0.95
mod7 <- lm(cwd~vpd_aug, data=mcf) # R2=0.53
mod8 <- lm(tmax~cwd, data=mcf) # R2=0.49

# summary info on TSLF adn elevation for the manuscript
mcf %>% dplyr::summarise(min = min(tslf),
                         mean = mean(tslf),
                         median = median(tslf),
                         max = max(tslf), 
                         min_elev = min(dem_10m_zaca),
                         mean_elev = mean(dem_10m_zaca),
                         max_elev = max(dem_10m_zaca))

```
surprisingly, far fewer variables are strongly correlated with each other and elevation than I would've have thought.

@@

###... Stepwise Variable Selection (VSURF)

@@

```
run 1 results: 
prediction step, variables selected:all

@@

*removed aug_max_vpd2006 and precip_2006 and reran VSURF*

run 2 results: 
interp step: "vpd_aug"      "slope"        "rain"         "tmax"         "tmin_jan"     "tmin_jan2007"

@@

@@

# select variables to be used in the model 
mcf_model3 <- mcf %>% 
  dplyr::select(rdnbr_qualitative, tmin_jan2007, vpd_aug, cwd, tmax, rain, sr, slope, aspect_transformed, TWI, ndmi_2006, evi_2006, tslf) # not sure if fri and years so fire, whic sounds like Time Since Last Fire, are the same thing

@@

3 classes
mtry=9,min.node.size=3; VI is mostly stable!

###... Random Forest
```{r}
for (i in 1:10) {

@@

###... ROC/AUC
```{r}
# code: https://stats.stackexchange.com/questions/188616/how-can-we-calculate-roc-auc-for-classification-algorithm-such-as-random-forest
rfm_roc <-  roc(mcf_model$rdnbr_tc, rfm$votes[,2])
plot(rfm_roc)
auc(rfm_roc)
```

###... ALE
```{r}
mcf_ale <- mcf_model3[-which(names(mcf_model3) == "rdnbr_qualitative")]

# predictors 
nlm_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf$rdnbr_qualitative, type = "prob", class="NLM")
high_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf$rdnbr_qualitative, type = "prob", class="High")
tc_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf$rdnbr_qualitative, type = "prob", class="Type Converted")

#ndmi
nlm1 <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high1 <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("High") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc1 <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm1, high1, tc1, nrow=1)
ggsave(here::here("Graph Images", "mcf ndmi.jpg"))

#solar radiation
nlm2 <- plot(FeatureEffect$new(nlm_predictor, feature = "sr")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high2 <- plot(FeatureEffect$new(high_predictor, feature = "sr")) + ggtitle("High") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc2 <- plot(FeatureEffect$new(tc_predictor, feature = "sr")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm2, high2, tc2, nrow=1)
ggsave(here::here("Graph Images", "mcf sr.jpg"))

#precip
nlm3 <- plot(FeatureEffect$new(nlm_predictor, feature = "rain")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high3 <- plot(FeatureEffect$new(high_predictor, feature = "rain")) + ggtitle("High") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc3 <- plot(FeatureEffect$new(tc_predictor, feature = "rain")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm3, high3, tc3, nrow=1)
ggsave(here::here("Graph Images", "mcf precip.jpg"))

#tmax
nlm4 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmax")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high4 <- plot(FeatureEffect$new(high_predictor, feature = "tmax")) + ggtitle("High") + labs(x="Max August Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc4 <- plot(FeatureEffect$new(tc_predictor, feature = "tmax")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm4, high4, tc4, nrow=1)
ggsave(here::here("Graph Images", "mcf tmax.jpg"))

#tmin jan 2007
nlm5 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmin_jan2007")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high5 <- plot(FeatureEffect$new(high_predictor, feature = "tmin_jan2007")) + ggtitle("High") + labs(x="Min 2007 January Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc5 <- plot(FeatureEffect$new(tc_predictor, feature = "tmin_jan2007")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm5, high5, tc5, nrow=1)
ggsave(here::here("Graph Images", "mcf tmin_jan2007.jpg"))

#vpd aug
nlm6 <- plot(FeatureEffect$new(nlm_predictor, feature = "vpd_aug")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high6 <- plot(FeatureEffect$new(high_predictor, feature = "vpd_aug")) + ggtitle("High") + labs(x="Max August VPD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc6 <- plot(FeatureEffect$new(tc_predictor, feature = "vpd_aug")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm6, high6, tc6, nrow=1)
ggsave(here::here("Graph Images", "mcf vpd_aug.jpg"))

#cwd
nlm7 <- plot(FeatureEffect$new(nlm_predictor, feature = "cwd")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high7 <- plot(FeatureEffect$new(high_predictor, feature = "cwd")) + ggtitle("High") + labs(x="CWD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc7 <- plot(FeatureEffect$new(tc_predictor, feature = "cwd")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm7, high7, tc7, nrow=1)
ggsave(here::here("Graph Images", "mcf cwd.jpg"))

#evi
nlm8 <- plot(FeatureEffect$new(nlm_predictor, feature = "evi_2006")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high8 <- plot(FeatureEffect$new(high_predictor, feature = "evi_2006")) + ggtitle("High") + labs(x="2006 EVI")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc8 <- plot(FeatureEffect$new(tc_predictor, feature = "evi_2006")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm8, high8, tc8, nrow=1)
ggsave(here::here("Graph Images", "mcf evi.jpg"))

#slope
nlm9 <- plot(FeatureEffect$new(nlm_predictor, feature = "slope")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high9 <- plot(FeatureEffect$new(high_predictor, feature = "slope")) + ggtitle("High") + labs(x="Slope")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc9 <- plot(FeatureEffect$new(tc_predictor, feature = "slope")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm9, high9, tc9, nrow=1)
ggsave(here::here("Graph Images", "mcf slope.jpg"))

#tslf
nlm10 <- plot(FeatureEffect$new(nlm_predictor, feature = "tslf")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high10 <- plot(FeatureEffect$new(high_predictor, feature = "tslf")) + ggtitle("High") + labs(x="TSLF")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc10 <- plot(FeatureEffect$new(tc_predictor, feature = "tslf")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm10, high10, tc10, nrow=1)
ggsave(here::here("Graph Images", "mcf tslf.jpg"))

#twi
nlm11 <- plot(FeatureEffect$new(nlm_predictor, feature = "TWI")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high11 <- plot(FeatureEffect$new(high_predictor, feature = "TWI")) + ggtitle("High") + labs(x="TWI")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc11 <- plot(FeatureEffect$new(tc_predictor, feature = "TWI")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm11, high11, tc11, nrow=1)
ggsave(here::here("Graph Images", "mcf twi.jpg"))

#aspect
nlm12 <- plot(FeatureEffect$new(nlm_predictor, feature = "aspect_transformed")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high12 <- plot(FeatureEffect$new(high_predictor, feature = "aspect_transformed")) + ggtitle("High") + labs(x="Aspect")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc12 <- plot(FeatureEffect$new(tc_predictor, feature = "aspect_transformed")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm12, high12, tc12, nrow=1)
ggsave(here::here("Graph Images", "mcf Aspect.jpg"))

ggarrange(nlm1, high1, tc1, tc1,nlm2, high2, tc2,tc1,nlm3, high3, tc3,tc1, nrow =3, ncol =4)
ggsave(here::here("Graph Images", "mcf ndm_sr_precip6.jpg"))

#ggarrange(nlm5, high5, tc5, nlm6, high6, tc6, nlm7, high7, tc7)

@@

# predictors 
nlm_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf_ale$rdnbr_qualitative, type = "prob", class="ULM")
high_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf_ale$rdnbr_qualitative, type = "prob", class="High")
tc_predictor <- Predictor$new(rfm, data = mcf_ale, y = mcf_ale$rdnbr_qualitative, type = "prob", class="Type Converted")

d = 7
#ndmi
nlm1 <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high1 <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + themet.margin = unit(c(d,1,1,1), "lines"))
tc1 <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm1, high1, tc1, nrow=1)
##ggsave(here::here("Graph Images", "mcf ndmi.jpg"))
#theme (panel.background = element_rect(width = 5))

@@

#vpd aug
nlm7 <- plot(FeatureEffect$new(nlm_predictor, feature = "vpd_aug")) + ggtitle("") + labs(x="Max August VPD")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))# + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high7 <- plot(FeatureEffect$new(high_predictor, feature = "vpd_aug")) + ggtitle("") + labs(x="Max August VPD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))# + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc7 <- plot(FeatureEffect$new(tc_predictor, feature = "vpd_aug")) + ggtitle("") + labs(x="Max August VPD")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm7, high7, tc7, nrow=1)
#ggsave(here::here("Graph Images", "mcf vpd_aug.jpg"))

@@

ggarrange(nlm1, nlm2,nlm3,nlm4,nlm5,nlm6,nlm7,nlm8,nlm9,nlm10,nlm11,nlm12, nrow = 3, ncol=4)
ggsave(here::here("Graph Images", "mcf all ulm_no sampsize.jpg"), width=8, height = 8)

ggarrange(high1,high2,high3,high4,high5,high6,high7,high8,high9,high10,high11,high12, nrow=3, ncol=4)
#ggsave(here::here("Graph Images", "mcf all high_no sampsize.jpg"), width=8, height = 8)

ggarrange(tc1,tc2,tc3,tc4,tc5,tc6,tc7,tc8,tc9,tc10,tc11,tc12, nrow=3, ncol=4)
ggsave(here::here("Graph Images", "mcf all tc_no sampsize.jpg"), width=8, height = 8)

@@

```{r}
pico <- read_csv("coulter_env_modified.csv") %>% 
  mutate(rdnbr_qualitative = case_when(
    rdnbr_2007 <= 640 ~ "NLM",
    rdnbr_2007 < 850 ~ "High",
    rdnbr_2007 >= 850 ~ "Type Converted")) %>%
  mutate(rdnbr_qualitative = as.factor(rdnbr_qualitative),
         rdnbr_qualitative = fct_relevel(rdnbr_qualitative, levels=c("NLM","High", "Type Converted"))) %>% 
  #filter(Mortality != "bigcone") %>% # 60 stands actually have big cones not pico
  dplyr::select(-Mortality, -type_converted, -ndvi_2006) %>% 
  na.omit(pico) %>%  # 56 stands have NA values (probs all very small stands)
   mutate(rdnbr_qualitative2 = case_when(
    rdnbr_qualitative %in% "High" ~ "High",
    rdnbr_qualitative %in% c("Moderate", "Low", "None") ~ "NLM")) %>% 
  mutate(rdnbr_qualitative2 = as.factor(rdnbr_qualitative2)) %>% 
  mutate(rdnbr_qualitative2= fct_relevel(rdnbr_qualitative2, levels=c("NLM", "High"))) %>% 
  mutate(aspect_transformed = (1-cos((2*pi*aspect_30m)/360))/2) %>% 
  mutate(rdnbr_tc = case_when(
    rdnbr_2007 < 850 ~ "Not_TC",
    rdnbr_2007 >= 850 ~ "TC"
  )) %>% 
  mutate(rdnbr_tc = as.factor(rdnbr_tc)) %>% 
  mutate(rdnbr_tc= fct_relevel(rdnbr_tc, levels=c("Not_TC", "TC"))) %>% 
  rename_all(funs(str_replace(., "_30m", "")))

@@

# predictors 
nlm_predictor <- Predictor$new(rfm, data = pico_ale, y = pico$rdnbr_qualitative, type = "prob", class="NLM")
high_predictor <- Predictor$new(rfm, data = pico_ale, y = pico$rdnbr_qualitative, type = "prob", class="High")
tc_predictor <- Predictor$new(rfm, data = pico_ale, y = pico$rdnbr_qualitative, type = "prob", class="Type Converted")

@@

#ndmi
nlm <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("High") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
ggsave(here::here("Graph Images", "pico ndmi.jpg"))
#theme (panel.background = element_rect(width = 5))

#solar radiation
nlm <- plot(FeatureEffect$new(nlm_predictor, feature = "insolation")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high <- plot(FeatureEffect$new(high_predictor, feature = "insolation")) + ggtitle("High") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc <- plot(FeatureEffect$new(tc_predictor, feature = "insolation")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
ggsave(here::here("Graph Images", "pico sr.jpg"))

#precip
nlm <- plot(FeatureEffect$new(nlm_predictor, feature = "rain")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high <- plot(FeatureEffect$new(high_predictor, feature = "rain")) + ggtitle("High") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc <- plot(FeatureEffect$new(tc_predictor, feature = "rain")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
ggsave(here::here("Graph Images", "pico precip.jpg"))
